%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% Andrew Choens - Resume
%% 
%% Based on Michael DeCorte's res.cls. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\documentclass[line, margin, 10pt]{res} 
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{colorlinks=false,linkbordercolor=red,linkcolor=green,pdfborderstyle={/S/U/W 1}}

\begin{document} 

\name{Andrew Choens, MSW - Resume}
%\address{26 Van Schoick Albany, NY 12208}
\address{andy.choens@gmail.com  (518) 275 - 5984}
\address{(518) 275 - 5984}

\begin{resume}

%  \vspace{.01in}
%  \begin{tabular} {c | c | c}
%    {\bf Policy Analyst} & {\bf Programmer} & {\bf Social Worker}
%  \end{tabular}
%  \vspace{.01in}

  \section{RESEARCH EXPERIENCE}

  %% Employer Template -----------------------------------------------------------
  %\employer{EmployerName}
  %\title{TitleName}
  %\dates{Dates01 - Dates02}
  %\location{Albany, NY}
  %\begin{position}
  %  PlaceholderTextIsHere
  %\end{position}

  %% IPRO ----------------------------------------------------------------------
  \employer{\href{http://ipro.org/}{IPRO}}
  \title{Healthcare Program Research Advisor}
  \dates{March 2014 - Current}
  \location{Albany, NY}
  \begin{position}
    Health Homes and Health Plans are managed care interventions
    designed to reduce utilization (cost) and improve outcomes for New
    York State Medicaid members with complex medical needs. Program
    participants are provided with a care manager who provides
    comprehensive case management services. Services range from
    addressing the members' medical needs to basic living and social
    needs. The theory is that providing a comprehensive case
    management will result in improved medical and functional outcomes
    for complex cases.

    Although the model is very promising; processes, outcomes and
    measurement are poorly understood. As an embedded consultant with
    the New York State Department of Health, I am resposible for
    leading a small team of analysts in developing an evaluation of
    Care Management in New York State and advising policy makers on
    how to best leverage these programs to improve the health of
    vulnerable New Yorkers.
  \end{position}

  % HZA --------------------------------------------------------------------------
  \employer{\href{http://www.hornbyzeller.com}{Hornby Zeller Associates}}
  \title{Policy Analyst}
  \dates{September 2007 - March 2014}
  \location{Troy, NY}
  \begin{position}
    Hornby Zeller Associates (HZA) is a consulting firm specializing
    in child welfare, elder care, juvenile justice and mental
    health. As a senior policy analyst, I was responsible for
    developing research hypotheses and methodology and providing
    support and mentoring for less experienced staff. Other
    responsibilities include data collection, structuring and
    analyzing data and disseminating results.

    Example projects:
    \begin{itemize}
    \item Program / Systems Evaluation: Arkansas (IV-E Waiver), West
      Virginia (Jacob's Law), Alaska (Mental Health Beneficiary Program)
    \item Time Study: Virginia, Westchester County, Wisconsin
    \item Accounting \& Title IV-E Funding: Wisconsin, Georgia, Mississippi
    \end{itemize}

    Accomplishments:
    \begin{itemize}
    \item Started an internship program and supervised intern.
    \item Developed templates and processes making it easier to
      automate the production of complex reports, improving staff
      efficiency.
    \item Provided ongoing training and support for junior staff
      learning how to manage and structure administrative and research
      data in tools such as PostgreSQL, SQL Server, R and SPSS.
    \item Mentored junior staff in of research methods and application
      of statistical tests.
    \item Introduced the use of version control for analytic code
      resulting in more reliable, reproducible results.
    \end{itemize}
  \end{position}

  % Coalition for the Homeless ---------------------------------------------------
  \employer{\href{www.coalitionforthehomeless.org}{Coalition for the Homeless}}
  \title{Principal Investigator}
  \dates{September 2006 - June 2007}
  \location{Albany, NY}
  \begin{position}
    Principal Investigator for an exploratory research project which
    established the existence of homeless men and women with
    borderline intellectual functioning in New York State homeless
    shelters.

    Accomplishments:
    \begin{itemize}
    \item Obtained IRB Approval.
    \item Demonstrated the validity of the Mini Mental Status Exam to
      identify homeless adults with borderline intellectual functioning.
    \item Recruited, trained and supervised a team of BSW students.
    \item Interviewed over 150 homeless New Yorkers. Successfully
      identified homeless adults with a historical diagnosis of
      borderline intellectual functioning.
    \item Presented results to the Assistant Commissioner
      of the Office of Mental Retardation and Developmental
      Disabilities\footnote{Now called the Office for People with
        Developmental Disabilities.}.
    \end{itemize}
  \end{position}


  \section{CLINICAL EXPERIENCE}

  % Catholic Charities -----------------------------------------------------------
  \employer{\href{http://www.ccrcda.org/}{Catholic Charities}}
  \title{Residential Habilitation Provider}
  \dates{October 2005 - September 2007}
  \location{Albany, NY}
  \begin{position}
    Delivered in-home services to Albany residents with mental
    retardation and other developmental disabilities. Services included
    family support, socialization skills and crisis counseling.
  \end{position}

  % Joseph's House ---------------------------------------------------------------
  \employer{\href{http://www.josephshousetroy.org}{Joseph's House \& Shelter}}
  \title{Advocate / Case Manager}
  \dates{September 2005 - May 2006}
  \location{Troy, NY}
  \begin{position}
    Worked with homeless guests to find housing and income in the form
    of jobs or social services such as SSD. Addressed other needs on a case-by-case
    basis. Developed a Guest Satisfaction Survey for the shelter. Surveyed
    guests in the shelter during the winter of 2005 - 2006.
  \end{position}

  % Ramapo for Children ------------------------------------------------------------
  \employer{\href{http://www.ramapoforchildren.org/}{Ramapo for Children}}
  \title{Teen Leadership Program Director}
  \dates{June 2003 - September 2005}
  \location{Rhinebeck, NY}
  \begin{position}
    Supervised an outdoor experiential program for teens with
    developmental disabilities and mental health
    diagnoses. Responsibilities included staff supervision and program
    development. Implemented a unique peer support program using
    conference calls. Led multi-day canoe trips on Indian Lake. Led family
    / team building activities including low and high ropes
    facilitation.
  \end{position}

  \section{RESEARCH TOOLS}

  \begin{tabular} {l l}
    {\bf Data Analysis:} R, Python, SAS, SPSS, Excel\\
    {\bf Data Management:} PostgreSQL, MySQL, SQL Server, Access\\
    {\bf Reproducible Research:} \LaTeX, Sweave, knitr, Org-Mode\\
  \end{tabular}

  \section{EDUCATION}
  \begin{tabular} {p{1.5in} p{2.125in} p{.75in}}
    Master of Social Work & The State University of New  York at Albany & Albany, NY 2007 \\
    Bachelor of International Affairs & Georgia Institute of
    Technology & Atlanta, GA 2002 
  \end{tabular}

  \vspace{.25in}
  Updated: 2015-02-03 \\
  \LaTeX version of this document available at:
  \href{https://github.com/Choens/Resume/}{https://github.com/Choens/Resume/}

  \vspace{.125in} 

\end{resume}

\end{document}
