
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% Andrew Choens - Example Projects
%% 
%% Based on Michael DeCorte's res.cls. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\documentclass[line, margin, 10pt]{res} 
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}

\hypersetup{colorlinks=false,linkbordercolor=red,linkcolor=green,pdfborderstyle={/S/U/W 1}}


\begin{document} 

% \name{Andy Choens, MSW - Example Projects}
% \address{156 Willow Street\\Guilderland, NY 12084}
% \address{(518) 275-5984\\andy.choens@gmail.com}

\name{Andrew Choens, MSW - Example Projects}
%\address{26 Van Schoick Albany, NY 12208}
\address{andy.choens@gmail.com}
\address{(518) 275 - 5984}

\begin{resume}

  \section{Hornby Zeller Associates}

  {\bf Mental Health Trust Beneficiary Study Update: 2013} \\
  {\bf Alaska Department of Corrections}  \\
  Conducted onsite case reviews and interviews of Trust beneficiaries
  along with data analysis of other social services programs to
  determine the extent to which individuals with untreated mental
  health problems may be kept out of the criminal justice system and
  in treatment, as well as to reduce their rate of recidivism.

  {\bf Evaluation of Title IV-E Waiver: 2013 - 2017 (Expected
    Completion Date)} \\
  {\bf Arkansas Department of Human Services, Division of Children and
    Family Services} \\
  Co-managed a multi-year evaluation of the implementation of a
  program designed to improve placement stability of youth.  Developed
  a logic model, protocol and tools to measure program fidelity,
  outcomes and cost-neutrality. Conducted data analysis using the
  SACWIS data.

  {\bf Prevent Child Abuse Iowa, Iowa Child Abuse Prevention Program -
    Community Based Child Abuse Prevention: 2013} \\
  {\bf Iowa Department of Human Services} \\
  Conducted data analysis of the Iowa Family Protective Factors survey used
  to measure change through a pre- and post-test. 

  {\bf Workload Study: 2012} \\
  {\bf Alaska Office of Children's Services}\\
  Conducted onsite interviews and focus groups of agency staff to
  identify activities and preliminary ways for support staff to provide
  additional assistance to front line caseworkers. Led the training of
  local participants through a series of webinars. Conducted data
  analysis of time available for case work and time needed to handle a
  case. Assisted in the update of time caseworkers require to handle
  cases. 

  {\bf Evaluation of Jacob's Law Implementation} \\
  {\bf West Virginia Department of Health and Human Resources} \\
  Led the data analysis component of an evaluation aimed at addressing
  the placement stability needs of foster care children age four to
  ten with difficult behaviors. Developed a web-based Child and
  Adolescent Needs and Strength assessment tool for case managers to
  use to identify service needs and measure progress. Participated in
  meetings with the Steering Committee guiding the project. 2011 -
  2014.

  {\bf Pahrump Office Review: 2011 - 2012}  \\
  {\bf Nevada Department of Human Services, Division of Children and
    Family Services} \\
  Conducted case record reviews of investigative, protective and
  foster care cases for an evaluation which focused on Nye County's
  adherence to policies and practices and its ability to provide for
  the safety, permanency and well-being of children.

  {\bf Children's Rights, M.D. v. Perry Litigation: 2011 - 2012} \\
  {\bf Texas} \\
  Formulated the sampling methodology used to select cases for a
  comprehensive case record review assessing the practices of
  caseworkers for children in permanent managing conservatorship.

  {\bf Sebastian Study: 2011}  \\
  {\bf Arkansas Department of Human Services, Division of Children and
    Family Services} \\
  Analyzed data from case record reviews of protective services and
  foster care cases collected to help identify the reasons for the
  county's high caseloads.

  {\bf Evaluation Services for Family Helpline, Family Navigator and
    Post Adoption/Post Guardianship Services: 2010 - 2012} \\
  {\bf Nebraska Department of Health and Human Services, Division of
    Children's Behavioral Health} \\
  Conducted data analysis of case record review information collected
  from the Family Navigator and Right Turn programs as well as that of
  the quarterly data extracts for both programs.

  {\bf Financial Assessment: 2010 - 2012} \\
  {\bf Mississippi Department of Human Services, Division of Family
    and Children Services} \\
  Conducted an analysis of the Divisions' SACWIS data to determine if
  additional Title IV-E and Title XIX federal funding is available to
  support DFCS programs.  Assessed the Random Moment Sampling process
  to determine its efficiency and capacity to maximize federal
  funding. Developed an automated process to identify and quantify
  maintenance and medical related costs for retroactive Title IV-E and
  XIX claiming, respectively.

  {\bf Strategic Prevention Framework State Incentive Grant: 2009 - 2011} \\
  {\bf Maine Department of Health and Human Services} \\
  Generated county-level reports for grant participants, using 2004,
  2006 and 2008 MYDAUS datasets in the evaluation of Maine's Strategic
  Prevention Framework Incentive Grant at the state, community and
  program levels.

  {\bf Division of Child Welfare, Random Moment Sampling Methodology
    for Claiming Title IV-E Allowable Administrative Costs} \\
  {\bf Colorado Department of Human Services - 2010 - 2012} \\
  Conducted interviews with Child Placement Agency (CPA) directors to
  better understand the contracting and rate setting processes for
  foster care children placed into the care of CPAs. Assisted in the
  development of the automated Random Moment Sampling web-based
  application, automating the percentage calculation of eligible Title
  IV-E administrative activities to be applied in calculating the
  quarterly claim for Title IV-E funding of allowable CPA
  activities.

  {\bf Quality Assurance Unit: 2010 - 2013} \\
  {\bf Arkansas Department of Human Services, Division of Children and
    Family Services} \\
  Conducted case record reviews, interviewed contract staff and their
  DCFS clients and assessed the findings of the case record reviews
  and CHRIS data as a part of the contract monitoring functions of the
  unit. Drafted reports detailing the extent to which contractors
  satisfied contract performance standards and met the needs for
  children served.

  {\bf Overdue Investigations: 2009} \\
  {\bf Arkansas Department of Human Services, Division of Children and Family
    Services} \\
  Participated in a statewide review of overdue investigations assessing what actions
  caseworkers should take to complete the investigations using defined
  criteria.

  {\bf Administrative Case Reviews: 2009} \\
  {\bf Arkansas Department of Human Services, Division of Children and
    Family Services} \\
  Conducted case record reviews of protective services and foster care
  cases to assess the quality of casework and identify barriers to
  successful outcomes for children. Interviewed caseworkers and/
  supervisors as part of the review of casework practice.

  {\bf Child Welfare Workload Study and Analysis: 2008 - 2011} \\
  {\bf Minnesota Department of Human Services, Division of Child Safety and
    Permanency} \\
  Participated in a workload study designed to measure resources
  required for the state and its counties to achieve positive safety and
  permanency outcomes for children served. Conducted data analysis of
  Time Study data for a sample of workgroups to measure time needed to
  handle specific types of workgroups and Random Moment Survey data to
  measure time staff have available for casework.  Developed the
  automated tool designed to correlate workload need to the ability to
  achieve positive outcomes and satisfy practice standards as well as an
  automated tool to generate workgroup type counts by unit.
  Participated in the onsite training of counties in the use of the tool
  and interpretation of its results.

  {\bf Workload Study: 2008 - 2009} \\
  {\bf Westchester County, NY Department of Social Services} \\
  Participated in focus groups as part of the
  development of an inventory of tasks and definition of case
  types. Assisted in training of county staff and monitoring of
  participation.  Conducted the data analysis measuring time needed to
  handle various types of cases and time caseworkers and supervisors
  have available for casework.

  {\bf Performance Audit: 2008 - 2009} \\
  {\bf Oklahoma House of Representatives, Oklahoma Department of Human
    Services} \\
  Conducted interviews of key stakeholders and assisted with case
  record reviews to assess the department's performance in terms of
  organizational and management structure especially as it relates to
  child welfare.  Assisted with the data analysis of surveys
  administered to department staff and resource families.

  {\bf Statewide Assessment of Systems and Services Pertaining to the
    Sexual and Physical Abuse of Children: 2008 - 2009} \\
  {\bf Connecticut Department of Children and Families} \\
  Conducted a literature review of services needed to serve sexually
  and physically abused children.  Assisted in the case record reviews
  and interviews with child advocacy center and multi-disciplinary
  team members.

  {\bf Juvenile Court Assessment: 2008} \\
  {\bf North Carolina Judicial Department} \\
  Compiled a catalog of relevant state and federal statutes,
  regulations and policies pertaining to the interstate compact for
  the placement of children.

  {\bf Interstate Placement of Children Review: 2008} \\
  {\bf Wisconsin Supreme Court, Director of State Courts Office, State
    Courts} \\
  Role in the Effective Interstate Placement of Children, Madison, WI:
  Created a catalog of federal and state statutes, regulations and
  policies involving the interstate placement of children.  Participated
  in case reviews of select cases across the state as well as interviews
  with key stakeholders.

  {\bf Title IV-E PIP Case Review: 2008} \\
  {\bf Georgia Department of Human Resources} \\
  Conducted on-site case reviews of Title IV-E eligibility cases to
  ensure determinations were correctly made and documentation was
  available in the file folder to support the determination as part of
  Georgia's Title IV-E Program Improvement Plan.

  {\bf Florida Abuse Hotline Prevention Referrals Assessment: 2008} \\
  {\bf Florida Department of Children and Families} \\
  Analyzed data collected to assess whether there
  was an alternative response to referrals to the Abuse Hotline and
  what the outcomes of those responses were.  Assisted in drafting the
  final report.

  {\bf Evaluation of Independent Housing with Services Program: 2008} \\
  {\bf Maine Office of Elder Services} \\
  Evaluated the results of surveys administered to consumers and
  resident service coordinators and assisted in drafting the summary
  report of findings.

  {\bf Title IV-E Penetration Rate Study: 2008} \\
  {\bf Georgia Department of Human Resources} \\
  Developed a tool for conduct of a review of training contracts to
  identify opportunities for increased IV-E funding.  Participated in
  the review of contracts with universities and colleges, along with
  their curricula, to identify programs eligible for Title IV-E
  funding.

  {\bf Needs-based Planning and Budgeting and CFSR Support: 2007 - 2013} \\
  {\bf Pennsylvania Department of Public Welfare, Office of Children,
    Youth and Families} \\
  Participated in the analysis of focus groups conducted as part of
  the self-assessment for the second round of Child and Family
  Services Reviews.  Assisted in the identification of key highlights
  in regard to safety, permanency and CFSR measure performance on a
  county-by-county basis as part of the production of semi-annual
  county packages.  Developed presentations for county-specific and
  statewide trainings designed to provide guidance in the use of the
  county packages in decision-making.

  \vspace{1in}
  \LaTeX version of this document available at: \emph{https://github.com/Choens/Resume/}

\end{resume}

\end{document}
