%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Andrew Choens - Resume
%%
%% Based on Michael DeCorte's res.cls.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[line, mm, 10pt]{res}
\usepackage[dvipsnames]{xcolor}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage[margin=1.0in]{geometry}

\hypersetup{
  colorlinks=true,
  linkcolor=Blue,
  linkbordercolor=Blue,
  pdfborderstyle={/S/U/W .5}
}

\begin{document}

\name{Andrew Choens, MSW - Resume}
\address{\href{mailto:andy.choens@gmail.com}{andy.choens@gmail.com}}
\address{\href{tel:(518) 275-5984}{(518) 275-5984}}

\begin{resume}

%  \vspace{.01in}
%  \begin{tabular} {c | c | c}
%    {\bf Policy Analyst} & {\bf Programmer} & {\bf Social Worker}
%  \end{tabular}
%  \vspace{.01in}


% \section{INTRODUCTION:}

% Ever since I can remember, I have been drawn to computer science and math, yet I was equally drawn to an understanding of politics, health care, mental health, and how the world works. For much of my life, these felt like competing interests because most computer science jobs are about selling services, ads, and clicks. While earning my MSW at SUNY Albany, I was given an opportunity to serve as the Principal Investigator for a research project on homelessness in New York State. The Coalition for the Homeless didn't have any analytical or data support, so I had to figure out how to gather the data, store the data, and analyze the data on my own. This experience became the catalyst for my professional career. I combined my degree and experience in social welfare to my life-long interest in computers and science to drive a career focused on the implementation, management, and improvement of human services programs.

% I work with state agencies, health care providers, and payers to use data to make important, often life changing, decisions. I connect my clients to their data by providing the tools, experience, or statistics to help them leverage their data to make informed, data driven decisions.

% I am an experienced team leader who can work with direct care staff and state agency leadership. I can help a client implement a new IT infrastructure, and I can help them develop key indicators of program success and identify how to improve the project's implementation.

\section{WORK EXPERIENCE:}

  %% Employer Template ---------------------------------------------------------
  %\employer{\href{URL}{NAME}}
  %\title{TitleName}
  %\dates{Dates01 - Dates02}
  %\location{Albany, NY}
  %\begin{position}
  %  PlaceholderTextIsHere
  %\end{position}


  % ---- ACPHS ----
  \employer{\href{https://www.acphs.edu/}{Albany College of Pharmacy \& Health Sciences}}
  \title{Adjunct Instructor}
  \dates{Spring 2018 - Present}
  \location{Albany, NY}
  \begin{position}
    I teach two undergraduate data classes. Both classes teach practical
    analytical skills, data management, and R programming. 
    
    \begin{itemize}
      \item[1.] "Intro To Data" introduces students to the R programming
      language. The class builds on the knowledge gained in the required statistics course and introduces fundamental R programming skills such as data import, visualization, and single table data transformations (filter, group by). Students also learn how to build and interpret linear and logistic regression models.
      \item[2.] "Applied Data Science" builds on Intro to Data. This project-based course introduces students to a synthetic EHR data set which is used to demonstrate how EHR data can be used to build an actionable analysis. Applied Data Science introduces more advanced R programming and project management skills. Students are introduced to relational data using dplyr functions. Students learn how to build a classifier model using decision trees and random forests.
    \end{itemize}
  
    Both classes include readings and discussions which are "Beyond the
    Numbers". These discussions cover topics intended to broaden students
    understanding of the opportunities and risks of data in our society. Topics
    include HIPAA, privacy laws beyond HIPAA, sources of bias in data, ethics in
    analytics, etc.

    Both classes give students the opportunity to use data and statistics to understand the world. Intro to Data applies this broadly and uses data to discuss current issues such as police shootings. Applied Data Science takes a more business-centric approach and teaches students how to use data to drive administrative/business decisions with data.
  \end{position}


  % ---- NYSTEC -----
  \employer{\href{https://www.nystec.com}{New York State Technology Enterprise Corporation (NYSTEC)}}
  \title{Consultant/Analyst}
  \dates{January 2023 - Present}
  \location{Albany, NY}
  \begin{position}
    The New York State Technology Enterprise Corporation is a technology
    consulting firm which provides services and guidance for the Federal and
    state governments, as well as local government agencies in New England. Since joining NYSTEC in 2023 I have worked with New York State agencies including:

    \begin{itemize}
    \item \textbf{Department of Health (DOH):} I work with with various DOH units within the Division of Health Plan Contracting and Oversight (DHPCO). I am responsible for a growing number of State and Federal reporting products including the annual Medicaid Managed Care Enrollment Report for Centers for Medicare and Medicaid (CMS). Analyses are based on Medicaid claims data, custom eMedNY integrations, and data provided by other State agencies. In my time with Mainstream Managed Care Systems Unit, I have dramatically improved the processing efficiency of case transfers from NySOH, improved the team's handling of Third Party Liability data, and improved the team's insight into the impact their work has on the overall Medicaid system. 
    \item \textbf{Division of Homeland Security and Emergency Services (DHSES):} I am responsible for developing a ICS/OT threat intelligence framework able to rapidly drive understanding and inferences of threats in New York State using a combination of public and secure data sources.
    \item \textbf{Office of Child and Family Services (OCFS):} Developed a new case management tool and operational dashboard for the OCFS Interagency Resolution Unit. This improved insight into how the unit was operating and allowed the unit to better communicate with its stakeholders and improve operational efficiency. Improved the team's ability to track and demonstrate its impact within OCFS.
    \end{itemize}
    
    I work in NYSTEC's Data Services and Management (DSM) team which provides analytical and consultative services. Within this team I work on improving the team's operational efficiency through mentoring, providing ongoing education regarding programming and statistics, and provide ad hoc support to other parts of the company. For example, we recently developed a new protocol for state agencies looking for guidance de-identifying and releasing publicly useful data in a way that can be shown to protect individual privacy. 
  \end{position}


  % ---- Charlie Health ----
  % \employer{\href{https://www.charliehealth.com}{Charlie Health}}
  % \title{Engineering Manager, Data}
  % \dates{July 2022 - December 2022}
  % \location{Remote, USA}
  % \begin{position}
  %   Charlie Health is a mental health provider which delivers
  %   remote-first Intensive Outpatient Care (IOC) to youth and young adults. 
    
  %   I supervised the nascent data engineering team. We supported business
  %   operations by democratizing access to Charlie Health's data. We implemented
  %   a process to slowly transition the operations team from a workflow driven by
  %   Google Sheets, to more automated processes using Snowflake and BI tools such
  %   as Tableau. By providing automated access to the data and reporting, we gave
  %   the operations team the time they needed to actually lead the operation of
  %   the company. 
  % \end{position}

  % \newpage

  % ---- Acuitas Health ----
  \employer{\href{http://www.acuitashealth.com/}{Acuitas Health}}
  \title{Data Science and Engineering Leader}
  \dates{September 2017 - June 2022}
  \location{Troy, NY}
  \begin{position}
    Acuitas was a population health services organization which helped primary
    care providers succeed in value based contracts with health insurance
    companies. As the leader of the Department of Data Science and Engineering I
    led the implementation of data-driven services and products. The team I led:
    
    \begin{itemize}
      \item developed a set of process and procedures for the development of
      high quality, validated, data deliverables including reports and
      statistical models
      \item hired a diverse team of analysts and data scientists
      \item trained the team in our process and procedures
      \item integrated our workflows with our Health Catalyst partners
      \item implemented technologies such as Posit Connect on top of the Health
      Catalyst ecosystem to provide consistent, reproduce results across a
      diverse range of data products
      \item built a Master Data Management (MDM) system able to accurately track patient interactions across payers and providers to improve analytics and patient outcomes
    \end{itemize}

    During my time with Acuitas, we integrated dozens of EHR, billing, and
    claims systems into a vendor neutral framework which enabled us to provide data products to clients regardless of their internal tech stack. Notable data products provided include:

    \begin{itemize}
      \item Federal HEDIS reports and tooling to identify opportunities to
      improve HEDIS scores
      \item Models and reports to assess the accuracy of patient HCC scores
      \item Dashboard to enable leadership to monitor provider efficiency
      \item Models to identify high-risk patients such as patients at risk of
      falling
    \end{itemize}
  
    Although I am proud of the accomplishments listed above, the team culture we created is the part I will always remember first. The time/cost pressures placed on the Acuitas team were immense. In spite of that reality, we developed a culture of teamwork and trust which helped us support each other through a pandemic and consistently deliver complex data products on aggressive timelines inside a broader business culture which was neither open nor supportive.
  \end{position}


  % ---- PCG ----
  \employer{\href{http://www.publicconsultinggroup.com/health/staffingsolutions/index.html}{PCG
      Staffing Solutions Organization - \\ New York State Department of Health}}
  \title{Healthcare Program Advisor}
  \dates{July 2017 - August 2017}
  \location{Albany, NY}
  \begin{position}
    PCG won the contract renewal from IPRO. In July all IPRO staff on the
    contract were moved to PCG to maintain continuity. I continued to report to
    the same DOH staff person and had the same responsibilities until I left in
    August.
  \end{position}


  % ---- IPRO ----
  \employer{\href{http://ipro.org/}{IPRO (Island Peer Review Organization) - \\ New York State Department
      of Health}}
  \title{Healthcare Program Research Manager}
  \dates{March 2014 - June 2017}
  \location{Albany, NY}
  \begin{position}
    Embedded consultant with the New York State Department of Health. Worked in the Office of Quality and Patient Safety (OCFS). My primary responsibility was for the internal evaluation and management of reporting in support of the New York State Health Homes initiative. I worked closely with both the
    external program evaluators and internal DOH stakeholders to understand the
    impact and effectiveness of Health Home care management programs and how to improve them. For example, developed a model which identified risk factors for Health Homes not enrolling members after a lengthy (and costly) outreach effort.
  \end{position}

  
  % ---- Hornby Zeller Associates ----
  \employer{Hornby Zeller Associates}
  \title{Policy Analyst}
  \dates{September 2007 - March 2014}
  \location{Troy, NY}
  \begin{position}
    Hornby Zeller Associates (HZA) was a consulting firm specializing in child
    welfare, elder care, juvenile justice, and mental health. 
    
    I was responsible for developing research hypotheses and methodologies and
    providing support and mentoring to junior staff. Other responsibilities
    include data collection, management and analysis of research data and
    dissemination of results. 
    
    I also initiated a transition from a workflow based on Access and SPSS to
    one based on Microsoft SQL Server and R which began the company's transition
    to reproducible reporting. The end result of this transition was improved
    accuracy and reduced timelines to report completion.
  \end{position}


  % ---- Coalition for the Homeless ----
  \employer{\href{www.coalitionforthehomeless.org}{Coalition for the Homeless}}
  \title{Principal Investigator}
  \dates{September 2006 - June 2007}
  \location{Albany, NY}
  \begin{position}
    Principal Investigator for an exploratory research project which established
    the existence of homeless men and women with borderline intellectual
    functioning in New York State homeless shelters.
  \end{position}



  % \newpage
  % \section{CLINICAL SOCIAL WORK EXPERIENCE:}


  % % ---- Catholic Charities ----
  % \employer{\href{http://www.ccrcda.org/}{Catholic Charities}}
  % \title{Residential Habilitation Provider}
  % \dates{October 2005 - September 2007}
  % \location{Albany, NY}
  % \begin{position}
  %   Delivered in-home services to Albany residents with mental
  %   retardation and other developmental disabilities. Services included
  %   family support, socialization skills, and crisis counseling.
  % \end{position}


  % % ---- Josephs House ----
  % \employer{\href{http://www.josephshousetroy.org}{Joseph's House \& Shelter}}
  % \title{Advocate / Case Manager}
  % \dates{September 2005 - May 2006}
  % \location{Troy, NY}
  % \begin{position}
  %   Worked with homeless guests to find housing and income in the form of jobs
  %   or social services such as SSD and addressed other needs on a case-by-case
  %   basis.
  % \end{position}


  % % ---- Ramapo ----
  % \employer{\href{http://www.ramapoforchildren.org/}{Ramapo for Children}}
  % \title{Teen Leadership Program Director}
  % \dates{June 2003 - September 2005}
  % \location{Rhinebeck, NY}
  % \begin{position}
  %   Supervised an outdoor experiential program for teens with developmental
  %   disabilities and mental health diagnoses. Responsibilities included staff
  %   supervision and program development. Implemented a unique peer support
  %   program for high-risk teens using conference calls.
  % \end{position}




  \section{PRESENTATIONS:}
  \begin{itemize}
    \item {\bf Health Analytics Summit (HAS):} {\href{https://www.youtube.com/watch?v=--vqwbJucPs}{Advanced Analytics for Medical Practices: Value-Based Care in the New Normal}}
    \item {\bf R In Epidemiology:} {\href{https://www.youtube.com/watch?v=-zhTXiiCj58}{Connecting Primary Care Providers to their own data}}
    \end{itemize}

    The above presentations are both available on Youtube and the
    links work in a digital version of this PDF.
  
  
  
  \section{EDUCATION:}
  \begin{tabular} {p{2.25in} p{2.75in} p{2in}}
    Master of Social Welfare & The State University of New York at Albany & Albany, NY 2007 \\
    Bachelor of International Affairs & Georgia Institute of Technology & Atlanta, GA 2002 \\
  \end{tabular}

  \section{DOMAIN-SPECIFIC WORK EXPERIENCE:}

  \begin{itemize}
    \item Analysis of cyber threat intelligence data (STIX, TAXII).
    \item Analysis of medical claims and electronic health records.
    \item Business support of Primary Care such as HEDIS reporting and Value Based Care
    \item Analysis \& evaluation of New York State Health Homes
    \item Analysis \& evaluation of state Child Welfare and Elder Care services
    \item Program implementation and improvement
    \item Improving business workflows
  \end{itemize}

  \section{TECHNICAL WORK EXPERIENCE:}

  \begin{itemize}
    \item {\bf Data Analysis:} Excel, Python, R, SAS, SPSS
    \item {\bf Database:} MySQL, PostgreSQL, Snowflake, SQL Server, Vertica
    \item {\bf BI:} Metabase, Posit Connect, Superset, Tableau, Voila, Qlik 
    \item {\bf Reproducible Research/Reporting:} \LaTeX, Pandoc, Quarto
    \item {\bf IT:} Linux server/workstation administration, Master Data Management, OCI container management 
  \end{itemize}

  % \vspace{.125in}

\end{resume}

\vspace{.25in}
Updated: \today \\
\LaTeX code for this document available at:
\href{https://github.com/Choens/Resume/}{https://github.com/Choens/Resume/}


\end{document}
