%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Andrew Choens - Cover Letter for PRA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{letter}
\usepackage[dvipsnames]{xcolor}
\usepackage[english]{babel}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkbordercolor=Blue,linkcolor=Blue, urlcolor=Blue}
\usepackage[margin=1.0in]{geometry}

\signature{Andy Choens}
\address{{\bf Applicant:} Andy Choens \\ {\bf Postion:} Research
  Associate \\ {\bf Email:} \underline{andy.choens@gmail.com} \\ Phone: (518) 275 - 5984}

\begin{document}
\begin{letter}{}

\opening{To whom it may concern,}

Thank you for the opportunity to apply for the Research Associate
position posted on your website. I am equal parts social worker,
business consultant, program evaluator, and computer programmer. I
believe my unusual combination of work experience, technical skills,
and professional motivation make me an excellent candidate for this
position and Policy Research Associate (PRA).

After graduating from SUNY Albany with a Masters in Social Welfare, I
dove headfirst into research and program evaluation, working for a
consulting firm called Hornby Zeller Associates (HZA) as a Policy
Analyst. HZA specializes in child welfare and juvenile justice
research and program evaluation. As a Policy Analyst, I participated
in projects in at least a dozen states and was involved in all aspects
of project planning and execution. I have attached a PDF file titled
"Andy Choens – Example Projects" which is from my days with HZA. This
document, which was written by my former employer, highlights the
breadth of my research experience in child welfare and juvenile
justice. This document also highlights my ability to where many hats. The
most recent Alaska project is a good example. For that project, I
interviewed State staff and toured Alaskan correctional facilities. I
also lead the data ETL from the State and the analysis of that data
once it was on HZA's server.

In my current role, as a Healthcare Program Manager, I am an embedded
consultant at the New York State Department of Health where I
supervise internal monitoring and evaluation of the New York State
Health Homes program. Once again, I find my ability to wear many hats
crucial to my success. I am the only member of the evaluation team
with mental health training and I am the only member of the team who
has ever worked in a human services organization as front-line
staff. Yet, I am also more familiar with relational data and database
admin tasks than others on the team. To wit, I led the development of
the field and technical specifications for the next generation Health
Home Care Management Reporting Tool (CMART). The first data submission
using this updated specification is due in May of this year.

I seek out complex jobs which diverse skill sets. Though the jobs may
seem dissimilar, a common thread ties them together. In every single
professional job I have ever had, I have endeavored to make my
community and my country a better place. Statistical analysis is not
an arcane, dispassionate science.  It is a tool for delivering better
services to those in need. It is a tool to making what is wrong,
right. Program evaluation and research are how I practice social
work. Judging by what I see on the PRA website, I think I could find a
niche there. If you would like to schedule an in-person interview, I
can be reached by email (\underline{andy.choens@gmail.com}) or phone
(518-275-5984).

\closing{Thank You For Your Consideration,}

\ps

\encl{Andy Choens - Resume.pdf, Andy Choens - Example Projects.pdf}

A copy of this cover-letter and attachments, in \LaTeX, can be found at: \\
\underline{https://github.com/choens/resume}

\end{letter}
\end{document}
